Word2vec learns effective distance of scientific co-affiliation

### 2020-01-28 paper/current/main.tex
Added plot showing predicted vs. actual using global orgs, not subsets

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\label{fig:gravity_performance}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
		\textbf{a.} embedding proximity (the cosine similarity between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
		Boxplots show distirbution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{e-f.} Predictions made for only pairs of organizations within the same country using embedding proximity outperform those made for geographic distance.
		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux between only pairs of organizations in different countries. 
	}
\end{figure}

@@

>>>>

%
% Figure - Gravity law performance
%
\begin{figure}[h!]
	\centering
	\label{fig:gravity_performance}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_performance.pdf}
	\caption{
		\textbf{Embedding proximity outperform and are more robust than geographic distance.}
		\textbf{a.} embedding proximity (the cosine similarity between vectors) explains more of the flux between organization pairs than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		\textbf{c-d.} Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{e-f.} Predictions made using model parameters learned from subset of same-country organization pairs. 
		Embedding proximity outperform those made for geographic distance.
		\textbf{g-h.} Embedding proximity also outperforms geographic distance when predicting flux using model parameters estimated from only pairs of organizations in different countries. 
		Predictions are not meaningfully different if estimates are learned on all pairs of organizations (Fig. S\ref{fig:supp:gravity_prediction_subsets}).
	}
\end{figure}

@@

%
% Figure - gravity predictions based on subset or global
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:gravity_prediction_subsets}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_different_fits.pdf}
	\caption{
		\textbf{Little difference between gravity predictions fit on all or subsets of data.}
		Predictions  of flux between organization pairs made using embedding proximity out-perform those made using geographic distance. 
		Boxplots show distribution of actual flux for binned values of predicted flux.
		Box color corresponds to the degree to which the distribution overlaps $x = y$.
		\textbf{a-b.} Predictions are made with parameter, estimating parameters from all pairs of organizatioons, making global predictions (as in Fig.~\ref{fig:gravity_performance}c), and showing only subsets of predictions for organization pairs in the same country (\textbf{a}) and in different countries (\textbf{b}).
		\textbf{c-d.} Predictions made by estimating gravity law parameters on subset of organizations in the same country (\textbf{c}) and different country \textbf{d}); 
		this is the same data as shown in Fig.~\ref{fig:gravity_performance}f and Fig.~\ref{fig:gravity_performance}h. 
	}
\end{figure}
